---
title: "LAb_3"
author: "Jasmine Sanchez, Erin Omyer, Adam Hayes, and Richard Park"
date: "January 30, 2019"
output: html_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
source("http://www.openintro.org/stat/data/cdc.R")
cdc <- as_tibble(cdc)
cdc
```

```{r}
ggplot(data = cdc) +
  geom_bar(mapping = aes(x = age, fill = genhlth)) +
  facet_wrap(~ smoke100)+
  labs(title = "Health Quality by Age for Smokers vs. Non-smokers")
```

```{r}
ggplot(data = cdc)+
  geom_bar(mapping = aes(x = genhlth, fill = genhlth), width = 1)+
  facet_wrap(~smoke100)+
  coord_polar()+
  labs(x = NULL, y = NULL, title = "Health Quality for Smokers vs. Non-smokers")

ggplot(data = cdc)+
  geom_bar(mapping = aes(x = genhlth, y = ..prop.., group = 1), width = 1)+
  facet_wrap(~exerany)+
  coord_polar()+
  labs(x = NULL, y = NULL, title = "Health Quality for People Who Don't Excercise vs People That Do ")

```

####Findings
Generally, the population of people that smoke have a much lower portion of people with 'excellent' health quality compared to non-smokers.  They also have a lower portion of people with 'very good' health quality, and higher portions of 'fair' and 'poor' health quality people. It also shows that of the people that excercise, the population has a much greater proportion of people with 'excellent' and 'ver good' health quality compared to those who don't excercise.
