---
title: "LAb_3"
author: "Jasmine Sanchez, Erin Omyer, Adam Hayes, and Richard Park"
date: "January 30, 2019"
output: html_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
source("http://www.openintro.org/stat/data/cdc.R")
cdc <- as_tibble(cdc)
cdc
```

##Question
How is people health affected by age and whether or not they smoke?

####Importance
This question is intriguing because people are constantly worried about their health, and what causes it to decrease and/or increase. People generally think that their health decrease with age, and that smoking will also decrease overall health quality. We wanted to investigate the validity of these general assumptions.
```{r}
ggplot(data = cdc) +
  geom_bar(mapping = aes(x = age, fill = genhlth)) +
  facet_wrap(~ smoke100)+
  labs(title = "Health Quality by Age for Smokers vs. Non-smokers")
```
####Conclusion
We concluded that general health tends to worsen with age with age with much lower portions of people registering 'excellent' health quality at higher ages.  Also, it is evident that overall health quality is lower for those who smoke cigarettes with higher portions of the populations registering with lower health quality compared to those who don't smoke.

####Recommendation
We would recommend that people try to avoid smoking cigarettes as much as possible, especially as they get older if they want to have better overall health quality. We would also recommend that people try to excercise more often because excercise is known to improve health quality.
```{r}
ggplot(data = cdc)+
  geom_bar(mapping = aes(x = genhlth, fill = genhlth), width = 1)+
  facet_wrap(~smoke100)+
  coord_polar()+
  labs(x = NULL, y = NULL, title = "Health Quality for Smokers vs. Non-smokers")

ggplot(data = cdc)+
  geom_bar(mapping = aes(x = genhlth, y = ..prop.., group = 1), width = 1)+
  facet_wrap(~exerany)+
  coord_polar()+
  labs(x = NULL, y = NULL, title = "Health Quality for People Who Don't Excercise vs People That Do ")

```

####Findings
Generally, the population of people that smoke have a much lower portion of people with 'excellent' health quality compared to non-smokers.  They also have a lower portion of people with 'very good' health quality, and higher portions of 'fair' and 'poor' health quality people. It also shows that of the people that excercise, the population has a much greater proportion of people with 'excellent' and 'ver good' health quality compared to those who don't excercise.



